\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-22 papers/jss/article.Rnw
update conclusion
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@817 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

%% an abstract and keywords
\Abstract{
Modern data collection and analysis pipelines often involve
a sophisticated mix of applications written in general purpose and
specialized programming languages.  Protocol Buffers are a popular
method of serializing structured data between applications---while remaining
independent of programming languages or operating system.  The
\CRANpkg{RProtoBuf} package provides a complete interface between this
library and the R environment for statistical computing.
%TODO(ms) keep it less than 150 words.
% Maybe add Jeroen's sentence:
% They offer a unique combination of features, performance, and maturity that seems
% particulary well suited for data-driven applications and numerical
% computing.
}
\Keywords{r, protocol buffers, serialization, cross-platform}
\Plainkeywords{r, protocol buffers, serialization, cross-platform} %% without formatting
%% at least one keyword must be supplied

@@

\section{Concluding remarks}
\label{sec:summary}
% TODO(mstokely): Get cibona approval for these two sentences before
% publishing.
Schema-less text formats such as CSV and JSON will continue to be
widely used in many contexts, but we hope that the availability of
\pkg{RProtoBuf} makes it easy for many mixed-language data analysis
pipelines to embrace schemas such as Protocol Buffers for type-safe
and performant data serialization between applications.

\pkg{RProtoBuf} has been heavily used inside Google for the past three
years by statisticians and software engineers.  At the time of this
writing there are more than XXX 30-day active users of RProtoBuf using
it to read data from and otherwise interact with other distributed
systems written in C++, Java, Python, and other languages.
\\

\emph{Other Approaches}
\\

>>>>

%% an abstract and keywords
\Abstract{
Modern data collection and analysis pipelines often involve
a sophisticated mix of applications written in general purpose and
specialized programming languages.  Protocol Buffers are a popular
method of serializing structured data between applications---while remaining
independent of programming languages or operating system.  The
\CRANpkg{RProtoBuf} package provides a complete interface between this
library and the R environment for statistical computing.
%TODO(ms) keep it less than 150 words.
% Maybe add Jeroen's sentence:
% JO: added this sentence to the conclustion, but could use it in abstract as well.
% They offer a unique combination of features, performance, and maturity that seems
% particulary well suited for data-driven applications and numerical
% computing.
}
\Keywords{r, protocol buffers, serialization, cross-platform}
\Plainkeywords{r, protocol buffers, serialization, cross-platform} %% without formatting
%% at least one keyword must be supplied

@@

\section{Concluding remarks}
\label{sec:summary}
% TODO(mstokely): Get cibona approval for these two sentences before
% publishing
Over the past decade, many formats have become available for interoperable
data exchange, each with their unique features, strengths and weaknesses. 
Text based formats such as CSV and JSON are easy to use and will likely 
remain popular among statisticians for many years to come. However, in the 
context of increasingly complex stacks and applications involving 
distributed computing and mixed language analysis pipelines, choosing a more 
sophisticated data interchange format will bring many benefits. 
Protocol Buffers offer a unique combination of features, performance,
and maturity that seems particulary well suited for data-driven 
applications and numerical computing.

The \pkg{RProtoBuf} package implements functionality to generate, 
parse and manipulate Protocol Buffer messages in R. We hope that 
this package will make Protocol Buffers more accessible to the R 
community, and contributes towards better integration of R with
other software. \pkg{RProtoBuf} has been heavily used inside Google
for the past three years by statisticians and software engineers.
At the time of this writing there are more than XXX 30-day active
users of RProtoBuf using it to read data from and otherwise interact
with other distributed systems written in C++, Java, Python, and 
other languages.
\\

\emph{Other Approaches}

== JO: I don't really like this section here, it gives the entire paper a bit of a 
sour aftertaste. Perhaps we can mention performance caveats in the technical
sections? I think it's nicer to leave it at the above paragraphs.==
